---
title: "Statistics for the Brakeman git repository"
author: "Steve Wainstead"
date: "June 12, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(git2r)
library(dplyr)
library(ggplot2)
library(purrr)
library(lubridate)

options(stringsAsFactors = FALSE)
```

```{r cloning, include=FALSE}
# Note: the first time you run this .Rmd file RStudio will clone
# the 'brakeman' project into a local directory. It may appear that RStudio
# hangs for a bit since there's no output. To see the output change include=FALSE to
# include=TRUE above.
if (!file.exists('brakeman-from-github')) {
  clone('https://github.com/presidentbeef/brakeman.git', 'brakeman-from-github')
}
```

```{r load-repo}

repo <- repository('brakeman-from-github')
# 285 is about 10% of the commits, as I write.
# I believe we get the commits from newest to oldest from git2r.
commits_10pct = repo %>% commits(n = 285)
commits_all = repo %>% commits()
```

Make a dataframe from our ten percent of the commits...

```{r get-10pct-commits}
# Get relevant bits out of the list
# Thank you Nay San!
# https://stackoverflow.com/questions/44474707/how-to-create-new-list-of-an-object-attribute-from-a-list-of-those-objects
brakeman_ten_pct_df <-
  commits_10pct %>%
  map_df(
    ~ data.frame(
      name    = .@author@name,
      date    = .@author@when@time %>% as.POSIXct(origin="1970-01-01"),
      message = .@message
    )
  )

brakeman_ten_pct_df <- mutate(brakeman_ten_pct_df, weekday = weekdays(date))
brakeman_ten_pct_df$weekday <- factor(brakeman_ten_pct_df$weekday, levels= c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"))
```


```{r order-by-weekday, include=FALSE}
brakeman_ten_pct_df <- brakeman_ten_pct_df[order(brakeman_ten_pct_df$weekday),]
```
Now create a histogram of commits by day of the week.

```{r dow-10pct-histogram}
brakeman_ten_pct_df %>%
  group_by(weekday) %>%
  tally() %>%
  ggplot(aes(x = weekday, y = n)) +
  geom_bar(stat = "identity")
```

Now we'll pull in all commits from the Git repository:

```{r dow-commits-all}
commits_all_df <-
  commits_all %>%
  map_df(
    ~ data.frame(
      name    = .@author@name,
      date    = .@author@when@time %>% as.POSIXct(origin="1970-01-01"),
      message = .@message
    )
  )

commits_all_df <- mutate(commits_all_df, weekday = weekdays(date))
commits_all_df$weekday <- factor(commits_all_df$weekday, levels= c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"))
```

Now the same bar chart of commits by weekday:

```{r dow-histogram-all}
commits_all_df %>%
  group_by(weekday) %>%
  tally() %>%
  ggplot(aes(x = weekday, y = n)) +
  geom_bar(stat = "identity")
```

The first puzzle is why these bar charts look so different? Could it be the most recent 10% of commits have a different weekday distribution because the committers (project contributors) have changed over time?
